Linear analysis of the vertical shear instability in astrophysical disks

### 2015-01-22 numerical.tex
adding applications

We have also solved this problem with in the low-frequency 
approximation by setting $D\to\kappa^2$ in Eq. \ref{ode_w} (with $Q=W$). We
obtained very similar results, as expected for modes with
$|\sigma/\Omega_k|\ll1$.

@@

We have also solved this problem in the low-frequency approximation
using Eq. \ref{ode_w}---\ref{ode_Q} with the replacement
$D\to\kappa^2$. We again obtained very similar results.

>>>>

% We have also solved this problem with in the low-frequency 
% approximation by setting $D\to\kappa^2$ in Eq. \ref{ode_w} (with $Q=W$). We
% obtained very similar results, as expected for modes with
% $|\sigma/\Omega_k|\ll1$.

@@

% We have also solved this problem in the low-frequency approximation
% using Eq. \ref{ode_w}---\ref{ode_Q} with the replacement
% $D\to\kappa^2$. We again obtained very similar results.
